---
title: "Portfolio"
author: "Sebastian Nickel"
date: "September 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
```


  
## Geosampling
```{r geosamplingtab}
data.frame(Type=c("[Package](github.com/senickel/geosampling)","[Documentation](senickel.github.io/sampling_documentation)","[ShinyApp](https://blacksheep.shinyapps.io/samplingnairobi/)"),
           Description=c("R Package to conduct geosampling","Documentation and demonstration of geosampling","Demonstrating both sampling strategies for Nairobi")) %>% 
  kable()
```

  

## readKML Function
```{r tabreadkml}
data.frame(Type="[StackOverflow Answer](https://stackoverflow.com/a/51657844/2763996)",
               Description="When reading KML files on Windows, the Extended Data is not read. My answer provides a solution to this problem by opening the KML as an XML file.") %>% 
  kable()
```
  

## Paper: Towntwinning in the Baltic Sea Region
```{r twiningtab}

data.frame(Type=c("[Article](https://www.tandfonline.com/doi/abs/10.1080/01629778.2018.1447977)",
                  "[Replication Files](https://github.com/senickel/city-networks-BSR-data)",
                  "[ShinyApp](https://blacksheep.shinyapps.io/graph2png/)",
                  "[Package](https://github.com/senickel/DOTtoPNG)"),
           Description=c("Bussmann/Nickel 2018. Study about towntwinning networks in the Baltic Sea region. Towntwinning data scraped from Wikipedia.",
                         "Data and files to replicate graphs.",
                         "ShinyApp to export DOT graphs to png.",
                         "Code for exporting DOT graphs to png.")) %>% 
  kable()

```

The paper was submitted in the first half of 2014. However, when making last changes to graphs in early 2018, I noticed that exporting DOT graphs to png was not supported by the DiagrammeR package on Windows. Hence, I wrote a small package and developed a ShinyApp to be able to export graphs.
  
## Accessing Stata through R

```{r tabottakring}
data.frame(Type="[Package](github.com/senickel/ottakring)",
           Description="Access Stata through R without the necessity of writing any Stata code. (WIP)") %>% 
  kable()
```
  
  
## Paper: Lost in Aggregation

```{r lostinaggr}
data.frame(Type="[PDF](https://senickel.github.io/portfolio/resources/Paper - Lost in Aggregation.pdf)",
           Description="Conference Paper presented on EPSA 2018 and APSA 2017. Effect of different spatial aggregation on variables.") %>% 
  kable()
```


## Analysis: Malawi Boreholes
```{r boreholes}
data.frame(Type="[PDF](https://senickel.github.io/portfolio/resources/Memo - Water access in Malawi.pdf)",
           Description="Effect of distance and wealth on water access in Malawi.") %>% 
  kable()
```

## MCA-PCA modernization index
```{r pcapca}
data.frame(Type="[PDF](https://senickel.github.io/portfolio/resources/MCA-PCA - modernization index.pdf)",
           Description="Creating indices of survey variables with MCA and PCA.") %>% 
  kable()
```

